A decomposition Approach for solving the JSP using multi-shot ASP\thanks{Supported by organization x.}

### 2022-01-17 ICLP Paper/samplepaper.tex
update tables_2

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass{tlp} % \documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{helvet,times,courier}
\usepackage{listings}
\usepackage[inline]{enumitem}
\usepackage{adjustbox}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\lstset{numberbychapter=false,numbers=left,numberblanklines=false,basicstyle=\footnotesize\ttfamily,xleftmargin=5ex,breaklines=false}
\usepackage{multirow}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\begin{table}[t]
    \caption{Results for three sizes of job shop scheduling instances with different numbers of time windows using static machine-based EST decomposition \label{tab:Table01}}%
%    \mbox{~}\hfill
%    \resizebox{0.8\textwidth}{!}{%
%    \begin{minipage}{\textwidth}
    \centering
    \begin{tabular}{l l r r r r r}
    \hline
%       & {}        & \multicolumn{6}{c}{Group of Instances}  \\
    Window(s) & Comparison & 50$\times$15 & 50$\times$20 & 100$\times$20 \\

    \hline\\[-2.75mm]
    1                & Makespan             & 3542.1   & 3879.4	     &  46786.1 \\
                     & CPU(Sec)             & 1000.0	& 1000.0   & 1000.0	     	    \\
                     & Interrupted Calls    & 1.0	    & 1.0      & 1.0	       \\[1.5mm]

    2                & Makespan             & 3149.7   & 3479.4	      & 23977.5 \\
                     & CPU(Sec)             & 1000.0	    & 1000.0	   & 1000.0	      \\
                     & Interrupted Calls    & 2.0	    & 2.0      & 2.0	      \\[1.5mm]

    3                & Makespan             & \textbf{3083.8}   & 3290.5	    & 7201.5 \\
                     & CPU(Sec)             & 1000.0	    & 1000.0	   & 1000.0	      \\
                     & Interrupted Calls    & 3.0	    & 3.0      & 3.0	      \\[1.5mm]

    4                & Makespan             & 3110.7   & \textbf{3260.3}	   & 6288.7 \\
                     & CPU(Sec)             & 934.4	    & 944.9	   & 1000.0	      \\
                     & Interrupted Calls    & 3.6	    & 3.5      & 4.0	      \\[1.5mm]

    5                & Makespan             & 3213.6   & 3355.5    & 6106.1 \\
                     & CPU(Sec)             & 615.5	    & 583.4	   & 1000.0	      \\
                     & Interrupted Calls    & 2.7	    & 2.5      & 5.0	      \\[1.5mm]

    6                & Makespan             & 3225.3   & 3414.8	      & \textbf{6031.9} \\
                     & CPU(Sec)             & 243.8	    & 321.5	   & 1000.0	      \\
                     & Interrupted Calls    & 1.0	    & 1.6      & 6.0	      \\[1.5mm]

    7                & Makespan             & 3350.5   & 3540.3	      & 6094.1 \\
                     & CPU(Sec)             & 146.7	    & 161.4	   & 1000.0	      \\
                     & Interrupted Calls    & 0.6	    & 0.9      & 7.0	      \\[1.5mm]

    8                & Makespan             & 3378.5   & 3561.5	      & 6053.1 \\
                     & CPU(Sec)             & 81.0	    & 54.9	   & 1000.0	      \\
                     & Interrupted Calls    & 0.3	    & 0.2      & 8.0	      \\[1.5mm]

    9                & Makespan             & 3495.0   & 3720.7	      & 6095.9 \\
                     & CPU(Sec)             & 45.6	    & 38.0	   & 977.0	      \\
                     & Interrupted Calls    & 0.1	    & 0.2      & 8.2	      \\[1.5mm]

    10               & Makespan             & 3524.9   & 3793.1	      & 6234.0 \\
                     & CPU(Sec)             & 18.5	    & 33.3	   & 861.8	      \\
                     & Interrupted Calls    & 0.1	    & 0.1      & 7.9	      \\[1.5mm]

@@

\multirow{2}*{Strategy} & \multicolumn{3}{c}{50$\times$15} & \multicolumn{3}{c}{50$\times$20} & \multicolumn{3}{c}{100$\times$20}\\
    & Makespan & CPU(Sec) & IC & Makespan & CPU(Sec) & IC & Makespan & CPU(Sec) & IC \\
    \hline\\[-2.75mm]
    Static machine-based EST              & \boldmath{$3083.8$}  & $1000.0$   & $3.0$	& \boldmath{$3260.3$}      & $944.9$ & $3.5$ & \boldmath{$6031.9$} & $1000.0$ & $6.0$\\
    [1.5mm]

    Static time-based EST             & $3524.8$ & $1000.0$   & $2.0$	   & $3540.8$      & $1000.0$ & $2.0$ & $6964.4$ & $1000.0$ & $4.0$\\ 
    [1.5mm]

    Static time-based MTWR             & $3456.2$  & $1000.0$   & $2.0$	& $3561.0$      & $1000.0$ & $2.0$ & $7149.6$ & $1000.0$ & $4.0$\\ 
    [1.5mm]

    Dynamic machine-based EST             & $3098.4$  & $1000.0$   & $3.0$	& $3309.5$     & $1000.0$ & $3.3$ & $6115.1$ & $1000.0$ & $6.9$\\ 
    [1.5mm]

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass{tlp} % \documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{helvet,times,courier}
\usepackage{listings}
\usepackage[inline]{enumitem}
\usepackage{adjustbox}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\lstset{numberbychapter=false,numbers=left,numberblanklines=false,basicstyle=\footnotesize\ttfamily,xleftmargin=5ex,breaklines=false}
\usepackage{multirow}
\usepackage{comment}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\begin{comment}
\begin{table}[t]
    \caption{Results for three sizes of job shop scheduling instances with different numbers of time windows using static machine-based EST decomposition \label{tab:Table01}}%
%    \mbox{~}\hfill
%    \resizebox{0.8\textwidth}{!}{%
%    \begin{minipage}{\textwidth}
    \centering
    \begin{tabular}{l l r r r r r r r r r r}
    \hline
%       & {}        & \multicolumn{6}{c}{Group of Instances}  \\
    &  &  \multicolumn{10}{c}{Number of Time Windows} \\
    Instances & Comparison & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\

    \hline\\[-2.75mm]
    {50$\times$15}       & Makespan             & $3542.1$   & $3149.7$	     &  \boldmath{$3083.8$} & $3110.7$ & $3213.6$ & $3225.3$ & $3350.5$ & $3378.5$ & $3495.0$ & $3524.9$ \\
    & CPU(Sec)             & $1000.0$	& $1000.0$   & $1000.0$	 & $934.4$ & $615.5$  & $243.8$  & $146.7$ 	& $81.0$ & $45.6$ & $18.5$  \\
    & Interrupted Calls    & $1.0$	    & $2.0$      & $3.0$	& $3.6$  & $2.7$  & $1.0$  &  $0.6$  & $0.3$ & $0.1$ & $0.1$       \\[1.5mm]

    {50$\times$20}       & Makespan             & $3879.4$   & $3479.4$	      & $3290.5$  &  \boldmath{$3260.3$} &  $3355.5$ & $3414.8$ & $3540.3$  &  $3561.5$  & $3720.7$  & $3793.1$ \\
    & CPU(Sec)             & $1000.0$	    & $1000.0$	   & $1000.0$	  & $944.9$  & $583.4$  & $321.5$  &  $161.4$  & $54.9$  & $38.0$  & $33.3$     \\
    & Interrupted Calls    & $1.0$	    & $2.0$      & $3.0$	& $3.5$ & $2.5$  & $1.6$  & $0.9$  & $0.2$ & $0.2$  & $0.1$      \\[1.5mm]

    {100$\times$20}      & Makespan             & $46786.1$  &  $23977.5$  & $7201.5$ &  $6288.7$                & $6106.1$  &  \boldmath{$6031.9$} & $6094.1$ & $6053.1$ & $6095.9$  & $6234.0$  \\
    & CPU(Sec) & $1000.0$	    & $1000.0$	   & $1000.0$	   & $1000.0$	    & $1000.0$	& $1000.0$	& $1000.0$ & $1000.0$	    & $1000.0$	& $1000.0$            \\
    & Interrupted Calls    & $1.0$	    & $2.0$      & $3.0$	& $4.0$ & $5.0$  & $6.0$ & $7.0$ & $8.0$ & $8.2$ & $7.9$      \\[1.5mm]

    \\[-2.75mm]
    \hline
    \end{tabular}
   % }
%    \end{minipage}
% }
%    \hfill\hfill\mbox{~}
\end{table}}

\end{comment}

\begin{table}[t]
    \caption{Results for three sizes of job shop scheduling instances with different numbers of time windows using static machine-based EST decomposition \label{tab:Table01}}%
%    \mbox{~}\hfill
%    \resizebox{0.8\textwidth}{!}{%
%    \begin{minipage}{\textwidth}
    \centering
    \begin{tabular}{l l r r r r r r r}
    \hline
%       & {}        & \multicolumn{6}{c}{Group of Instances}  \\
    &  &  \multicolumn{7}{c}{Number of Time Windows} \\
    Instances & Comparison & 1 & 2 & 3 & 4 & 5 & 6 & 10 \\

    \hline\\[-2.75mm]

    {50$\times$15}       & Makespan             & $3542.1$   & $3149.7$	     &  \boldmath{$3083.8$} & $3110.7$ & $3213.6$ & $3225.3$ & $3524.9$ \\
    & CPU(Sec)             & $1000.0$	& $1000.0$   & $1000.0$	 & $934.4$ & $615.5$  & $243.8$  & $18.5$  \\
    & Interrupted Calls    & $1.0$	    & $2.0$      & $3.0$	& $3.6$  & $2.7$  & $1.0$  & $0.1$       \\[1.5mm]

    {50$\times$20}       & Makespan             & $3879.4$   & $3479.4$	      & $3290.5$  &  \boldmath{$3260.3$} &  $3355.5$ & $3414.8$ & $3793.1$ \\
    & CPU(Sec)             & $1000.0$	    & $1000.0$	   & $1000.0$	  & $944.9$  & $583.4$  & $321.5$   & $33.3$     \\
    & Interrupted Calls    & $1.0$	    & $2.0$      & $3.0$	& $3.5$ & $2.5$  & $1.6$  & $0.1$      \\[1.5mm]

    {100$\times$20}      & Makespan             & $46786.1$  &  $23977.5$  & $7201.5$ &  $6288.7$                & $6106.1$  &  \boldmath{$6031.9$}   & $6234.0$  \\
    & CPU(Sec) & $1000.0$	    & $1000.0$	   & $1000.0$	   & $1000.0$	    & $1000.0$	& $1000.0$	& $861.8$            \\
    & Interrupted Calls    & $1.0$	    & $2.0$      & $3.0$	& $4.0$ & $5.0$  & $6.0$ & $7.9$      \\[1.5mm]

@@

\multirow{2}*{Strategy} & \multicolumn{3}{c}{50$\times$15} & \multicolumn{3}{c}{50$\times$20} & \multicolumn{3}{c}{100$\times$20}\\
    & Makespan & Time & IC & Makespan & Time & IC & Makespan & Time & IC \\
    \hline\\[-2.75mm]
    M-Based EST (S)             & $3083.8$  & $1000.0$   & $3.0$	& \boldmath{$3260.3$}      & $944.9$ & $3.5$ & $6031.9$ & $1000.0$ & $6.0$\\
    [1.5mm]

    T-based EST (S)            & $3524.8$ & $1000.0$   & $2.0$	   & $3540.8$      & $1000.0$ & $2.0$ & $6964.4$ & $1000.0$ & $4.0$\\ 
    [1.5mm]

    M-based MTWR (S)        & \boldmath{$3060.3$}  & $1000.0$   & $3.0$	& $3287.9$      & $986.1$ & $3.9$ & \boldmath{$5948.6$} & $1000.0$ & $7.0$\\ 
    [1.5mm]

    T-based MTWR (S)            & $3456.2$  & $1000.0$   & $2.0$	& $3561.0$      & $1000.0$ & $2.0$ & $7149.6$ & $1000.0$ & $4.0$\\ 
    [1.5mm]

    M-based EST (D)            & $3098.4$  & $1000.0$   & $3.0$	& $3309.5$     & $1000.0$ & $3.3$ & $6115.1$ & $1000.0$ & $6.9$\\ 
    [1.5mm]
